### 2023-10-19 vesicle_code/docs/confinedMulti/response.tex

%%%%%%%%
\item In experiments, the channel is a slit. What do the authors expect
  from such a difference?

\noindent
{\bf Response:} We can compare Zhangli Peng's results, our simulations
look similar to what they observe in a 2D projection of their 3D
results. They call their geometry a `slit' geometry. This work is
published, so we can reference a particular figure from the paper.

%%%%%%%%
\item Finally, this study is interesting and provides new insights.
  However, I advise authors to improve the quantitative part of their
  results (variation with Ca or confinement or something else, phase
  diagram...) to be more relevant for a journal such as Soft Matter. I
  am waiting the new manuscript.

\noindent
{\bf Response:} A phase diagram is included in Figure~\ref{fig:Phase}.
We do not observe any dependence on the capillary number. We had a
discussion with a colleague who works on experiments
with a red blood cell passing through stenosis, where RBCs form a single line in the mid-plane of the channel.
 His experiments have shown that the
shape of the RBC inside this confined stenosis is independent over a
range of capillary numbers, as we report in Figure~\ref{fig:Phase}. For
this reason, we do not include this phase diagram in our manuscript. We have
started examining the dependence of these dynamics on other
dimensionless parameters such as the confinement ratio and the
floppy-to-stiff ratio. This will be a different focus and would distract
from the focus of this work.
\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{phaseDiagram.jpg}
  \caption{\label{fig:Phase} A phase diagram of a single vesicle in an unconfined
  nonlinear shear flow. The capillary number has no effect on the steady
  state shape of the vesicle.}
\end{figure}

@@

%%%%%%%%
\item Page 2, left column : the flow is assumed to be in the limit of
  zero Reynolds number : not the fluid

\noindent
{\bf Response:} Thank you for correcting this error. We have added the
word `flow' to the manuscript.

%%%%%%%%
\item The title is a bit misleading as the authors only consider the
  deflation equal to the one of RBC. However, as there is some conflict
  between capsules and vesicles as models of RBC, the title can be
  tolerated.

\noindent
{\bf Response:} We thank the referee for this comment. We did not change the title as the referee found it tolerable.
\end{enumerate}

### 2023-10-20 vesicle_code/docs/confinedMulti/response.tex

%%%%%%%%
\item The authors mention the phrase `size of lubrication layer' in the
  paper. They need to explicitly define this parameter. It could be
    confusing to a reader whether they talk about
    $|\gamma_{\mathrm{layer}}|$ or $w_{\mathrm{top}}$ and
    $w_{\mathrm{bottom}}$.

\noindent
    {\bf Response:} We have labelled $w_{\mathrm{top}}$ and
    $w_{\mathrm{bot}}$ in Figure 1. We have adjusted the text in Section
    2.4.

%%%%%%%%
\item The authors measure the tangential velocity at 4 points. They
  should provide some justification for this number. Also, it is
    advisable that in Figure 7, the authors use a different color for
    each velocity plot. The plot looks highly convoluted and does not
    convey the message clearly. Also, what are the bounds within which
    the authors call the tangential velocity to be constant in Figure 7?
    They should define a bound for the variation that could be
    considered constant. Moreover, in Figure 7, for the floppy vesicle,
    the authors see a large deviation for the tangential velocity. It
    doesn't seem like the velocity could be called `constant'. The
    authors should provide a more detailed explanation for this.

\noindent
    {\bf Response:} We calculated the tangential velocity of all $N =
    1024$ Lagrangian points for each of the three cases. Plotting all
    1024 lines in the manuscript would be uninformative. To prove this is
    the case, a plot of 32 of the tangential velocities is in Figure~\ref{fig:tangVel} of this document. 
%    
Instead we track the tangential velocity of each Lagrangian marker on
the vesicle membrane, measuring the spread in this tangential velocity
over the part of the period when the vesicle is inside the stenosis.
This spread, scaled by the velocity magnitude, is color-coded along the
membrane and is now part of Figure 7. The original plots showing the
tangential velocity of the four points are removed. For a tank-treading
vesicle, this scheme would give a membrane of a uniform color. On the
other hand, a non-uniformly colored membrane implicates the lack of
tank-treading in the vesicle membrane, which may also correspond to
significant deformations in the membrane.
%   
% Instead, in the document,
%  we report the average tangential velocity in the region $x \in
% [4,10]$, and report the spread of all tangential velocities from
%this mean value. 
More quantitatively, if this spread is less than 15\%, we would
characterize this as a tank-treading vesicle. Their spread is 1.2\% for
the stiff single-component vesicle, 12\% for the multicomponent case,
and 313\% for the floppy single-component case. Therefore, the floppy
single-component vesicle is not tank-treading, while the other two cases
are tank-treading. We have made this clear in the text.

\begin{figure}[ht]
  \centering
  \subfigimg[width=0.3\textwidth]{(a)}{figures/SC_treading_velocity_review.pdf}
  \subfigimg[width=0.3\textwidth]{(b)}{figures/SCp55_treading_velocity_review.pdf}
  \subfigimg[width=0.3\textwidth]{(c)}{figures/MCp5_treading_velocity_review.pdf}
  \caption{\label{fig:tangVel} The tangential velocity of 32 points of
  the (a) stiff single-component vesicle, (b) floppy single-component
  vesicle, (c) multicomponent vesicle. Note that these figures, and the
  version with four marker points, are excluded from the revised
  manuscript.}
\end{figure}

@@

\noindent
{\bf Response:} We initially explored cases where the single-component
vesicle became stuck, expecting that the multicomponent vesicle may pass
through the same geometry. We did not find any such cases.
However, we did observe other behaviors that differ between the two
cases, including the vesicle shape, tank treading velocity, lubrication
layer, and these comparisons are the focus of our manuscript. We defer
our response to the phase diagram point until comment number 6.

%

%%%%%%%%
\item In experiments, the channel is a slit. What do the authors expect
  from such a difference?

\noindent
{\bf Response:} We are interpreting this question as the reviewer asking
about 3D effects. In the literature, the 3D simulations of a red blood
cell through a 3D slit (see Lu and Peng,
https://doi.org/10.1063/1.5081057) has a 2D projection that looks
similar to our 2D simulations. In particular their right-most panel in
Figure 5(b) resembles Figures 10(d) and 10(e) in columns V and VI from
our paper. Other than the shape similarity of the 2D projection, we also
find that our excess pressure is of the same order for a similar flow
rate in a 3D case (http://dx.doi.org/10.1063/1.4817959).

@@

%%%%%%%%
\item Finally, this study is interesting and provides new insights.
  However, I advise authors to improve the quantitative part of their
  results (variation with Ca or confinement or something else, phase
  diagram...) to be more relevant for a journal such as Soft Matter. I
  am waiting the new manuscript.

\noindent
{\bf Response:} As shown recently by Agarwal and Biros
(http://www.doi.org/10.1103/PhysRevFluids.5.013603) (see Figure 18a),
when a vesicle is in a channel with strong confinement, there are at
most two different shapes a vesicle can take on for different capillary
numbers. They observe this for confinement ratios as large as 0.7, and
our examples have a confinement ratio closer to 2 (stronger
confinement). To verify this claim, we constructed a phase diagram for a
multicomponent vesicle in a unconfined non-linear shear flow by varying
the reduced area and the capillary number. We observe that the
multicomponent vesicle is more symmetric in shape than the
single-component vesicle for a wide range of capillary numbers and
reduced areas (Figure~\ref{fig:Phase}). Based on this, we speculate that
a phase diagram with strong confinement would be less interesting than
the single-component case, so we exclude a phase diagram in confinement.
%
%A phase diagram is included in Figure~\ref{fig:Phase}.
%We do not observe any dependence on the capillary number.

We have also discussed this topic with a colleague who works on
experiments with a red blood cell passing through stenosis, where RBCs
form a single line in the mid-plane of the channel. His experiments have
shown that the shape of the RBC inside this confined stenosis is
independent over a range of capillary numbers. For this reason, we focus
on the relationships between between the vesicle shape, lubrication
layer, excess pressure, and asymmetry relative to the midline.

We have started examining the dependence of the vesicle symmetry on
other dimensionless parameters such as the confinement ratio and the
floppy-to-stiff ratio. This will likely give rise to different phenomena
and analyses that would distract from the focus of this work.
\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{phaseDiagram.pdf}
  \caption{\label{fig:Phase} A phase diagram of a single multicomponent
  vesicle in an unconfined nonlinear shear flow. The capillary number
  has no effect on the steady state shape of the vesicle.}
\end{figure}

### 2023-10-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
adding last figure to rebuttal

\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
  \caption{\label{fig:Energy} \small The bending (blue), tension (red),
  and phase (green) energies of a (a) stiff single-component, (b)
  floppy single-component, and (c) multicomponent vesicle. The reduced
  area is $\alpha = 0.4$. Note that the single-component vesicles do not
  have a phase energy.} 
\end{figure*}
\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SC_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SCp55_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/MCp5_treading_velocity2.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:lubricationComposite} \small The lubrication layer
  thicknesses (red and blue), excess pressure (green), and
  tank-treading velocity of four Lagrangian points of a (a) stiff
  single-component vesicle, (b) floppy single-component vesicle, and (c)
  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
  three cases. 
  \textcolor{blue}{
  Also illustrated is the vesicle shape when its center of mass is
  located at $x=4$. Then, color represents the spread of the tangential
  velocity relative to the average tangential velocity, where the average
  is taken over the region $x \in [4,10]$. We characterize the stiff
  single-component and multicomponent vesicles as tank treading since
  the spread in the tangential velocity is below \%15, while the floppy
  single-component vesicle is not tank treading.
  }
%  Also illustrated is the vesicle shape and the four
%  Lagrangian points at the location indicated by the dash line.
  The black dashed line is the center line of the channel, and the arrow
  denotes the tank-treading direction. The percentage of the vesicle
  membrane that is below the center line is (a) 72\%, (b) 44\%, and (c)
  68\%.}
\end{figure*}

>>>>

\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
  \caption{\label{fig:Energy} \small The bending (blue), tension (red),
  and phase (green) energies of a (a) stiff single-component, (b)
  floppy single-component, and (c) multicomponent vesicle. The reduced
  area is $\alpha = 0.4$. Note that the single-component vesicles do not
  have a phase energy.} 
\end{figure*}
\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SC_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SCp55_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/MCp5_treading_velocity2.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:lubricationComposite} \small The lubrication layer
  thicknesses (red and blue), excess pressure (green), and
  tank-treading velocity of four Lagrangian points of a (a) stiff
  single-component vesicle, (b) floppy single-component vesicle, and (c)
  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
  three cases. 
  \textcolor{blue}{
  Also illustrated is the vesicle shape when its center of mass is
  located at $x=4$. Then, color represents the spread of the tangential
  velocity relative to the average tangential velocity, where the average
  is taken over the region $x \in [4,10]$. We characterize the stiff
  single-component and multicomponent vesicles as tank treading since
  the spread in the tangential velocity is below 15\%, while the floppy
  single-component vesicle is not tank treading.
  }
%  Also illustrated is the vesicle shape and the four
%  Lagrangian points at the location indicated by the dash line.
  The black dashed line is the center line of the channel, and the arrow
  denotes the tank-treading direction. The percentage of the vesicle
  membrane that is below the center line is (a) 72\%, (b) 44\%, and (c)
  68\%.}
\end{figure*}
